TODO: Funky active learning pun

### 2025-01-10 doc/paper.tex
Work on report and add cnn model and training pipeline
This was pain

This report focuses on comparing several query strategies for both pool-based and stream-based active learning. Experiments in this paper leverage the modular Active Learning framework (modAL)~\cite{danka_modalmodularactivelearning}, which simplified the implementation of active learning pipelines, includes multiple pre-implemented query strategies and is compatible with models from the Scikit-learn library~\cite{scikit-learn}. \\

@@

\section{Methods}\label{sec:methods}
\label{data_and_methods}
\subsection{Datasets}
\begin{itemize}
	\item MNIST and CIFAR describe
	\item processing steps \\
	MNIST: Vectorized, flattened (describe input size), normalized
\end{itemize}

\subsection{Models}
\begin{itemize}
	\item Logistic Regression: Details on implementation and hyperparameters, how were they chosen?
	\item same for CNN
\end{itemize}

@@

\section{Discussion}\label{sec:discussion}
Qualitative analysis: Why certain strategies perform better or worse in specific settings. Trends between simple models and complex models
\\
\\
Impact of initial dataset size
\\
\\
Most methods require knowledge about the balance of the dataset and might be disadvantageous to use in case of a disbalanced dataset. In real world scenarios, this is not known. \\
Only image-based datasets were tested. Not vector- or text-based.

>>>>

This report focuses on comparing several query strategies for both pool-based and stream-based active learning. Experiments in this paper leverage the modular Active Learning framework (modAL)~\cite{danka_modalmodularactivelearning}, which simplified the implementation of active learning pipelines, includes multiple pre-implemented query strategies and is compatible with models from the Scikit-learn library~\cite{scikit-learn}. \textcolor{red}{CNN implemented with PyTorch(ADD CITATION) and transformed with skorch~\cite{skorch} to make it compatible with modAL as it is only compatible with sklearn models.} \\

@@

\section{Methods}\label{sec:methods}
Several different datasets are used in the following experiments.
\subsection{Datasets}
MNIST is a dataset consisting of handwritten digits with 60.000 train samples and 10.000 test samples. Digits are size-normalized and centered in a $28 \times 28$ image~\cite{mnist}. Each digits belongs to one of 10 classes, corresponding from 0 to 9. \\
Upon loading the dataset, each image is vectorized, i.e. transformed from a $28 \times 28$ sized image-matrix to a vector of length $784$. Furthermore, each pixel contains a grayscale-value from 0 to 255. Pixel values are normalized to a range between 0 and 1 to provide a value range that works well with logistic regression. 
\\
\textcolor{red}{Here describe the validation split}
\\
\\
CIFAR-10 is a dataset which consists of 50.000 train- and 10.000 test-images. Each natural image belongs to one of 10 classes. Each class has exactly 5.000 train and 1.000 test images. The image-size is $32 \times 32$ pixels. 
\textcolor{red}{CIFAR preprocessing split and validation split}
\\
\\
Both used datasets are balanced, i.e. each class has roughly the same number of samples as any other class.

\subsection{Models}
\begin{itemize}
	\item Logistic Regression: Details on implementation and hyperparameters, how were they chosen?
	\item same for CNN: CrossEntropyLoss (combines Log Softmax and NLLoss in one single class)
\end{itemize}
Are models re-initialized after each new data points and newly trained or fine-tuned?

@@

\section{Discussion}\label{sec:discussion}
Qualitative analysis: Why certain strategies perform better or worse in specific settings. Trends between simple models and complex models
\\
\\
Impact of initial dataset size
\\
\\
Most methods require knowledge about the balance of the dataset and might be disadvantageous to use in case of a disbalanced dataset. In real world scenarios, this is not known. Both used datasets are balanced so the impact of query strategies on imbalanced datasets was not tested. \\
Only image-based datasets were tested. Not vector- or text-based.
